### 2019-10-10 paper/introduction.tex
Andrei's minor changes in the  Introduction

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation nuclear systems. These goals are; safety and reliability, economics, sustainability, non-proliferation and physical protection \cite{doe2002technology}. \glspl{MSR} have many advantages that consistent with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online reprocessing and refueling, excellent neutron economy and operation under ambient pressure \cite{siemer2015molten,rosenthal1970molten}. Therefore, in 2002 the \gls{MSR} has been chosen as one of the promising reactors by this forum \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel supposed to be in the form of liquid dissolved in molten salt (e.g., LiF or NaCl). This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly circulates through the core and allows transferring fission heat.

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250 MWth) was introduced by the \gls{CAS} \cite{li_optimization_2018}. The SD-TMSR is a graphite-moderated thermal-spectrum MSR. In the SD-TMSR the fissile and fertile elements are integrated into the same salt. In addition, the active core is divided into two zones, the radius of the fuel channels in the outer zone is modified to be larger than the radius of the fuel channels in the inner zone to improve the breeding ratio \cite{nuttin2005potential,li_optimization_2018}.

Basically, the \gls{MSR} has been designed to apply the Th/$^{233}$U fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,merle2004scenarios,rosenthal1970molten}. Hence, the fertile isotope $^{232}$Th is converted to the fissile isotope $^{233}$U, an isotope that is not exist in nature. Therefore it is required to examine available fissile materials (e.g., $^{235}$U and Pu) to replace the $^{233}$U in the startup fuel \cite{betzler2016modeling,zou2018transition}. The thorium fuel cycle transition can be achieved after reaching the doubling time\footnote{Time required to produce enough amount of $^{233}$U to trigger a new SD-TMSR.} of $^{233}$U.

Betzler, et al. discussed the simulation of the start-up of a MSBR unit cell with LEU (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial fissile materials \cite{betzler2016modeling}. They concluded that the plutonium vector extracted from LWR SF serves as the best alternative source to $^{233}$U thanks to the highest ratio of fissile isotopes \cite{betzler2016modeling}. Zou, et al. introduced two approaches for the thorium fuel cycle transition in \gls{TMSR}: in-core transition and ex-core transition. In the former way, the TMSR is launched with existing fissile material and thorium as a fertile material, then the bred $^{233}$U from thorium is rerouted into the core for criticality. In contrast, the latter way tends to store the bred $^{233}$U out of the core until there is enough amount to start a new TMSR \cite{zou2018transition}.
Meanwhile, Zou, et al. studied the transitioning to thorium fuel cycle in a small modular Th-based molten salt reactor (smTMSR) using TRUs as startup fuel. They concluded that the transition to thorium fuel cycle can be achieved in thermal smTMSR with a proper fuel fraction \cite{zou2018preliminary}.
Heuer, et al., discussed the transition characteristics of the \gls{MSFR} under different launching scenarios (e.g., enriched uranium and TRU) \cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the MSRs with fissile materials alternative to $^{233}$U. Many of these researches focus on the fast-spectrum MSRs \cite{ashraf2019modeling,ashraf2018nuclear,heuer2014towards,fiorina2013investigation}, while little focus on thermal-spectrum MSRs \cite{betzler2016modeling,zou2018preliminary,zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other fissile materials (except $^{233}$U) not found in the literature. Therefore, the main object of the present paper is to discuss the simulation of the operation of \gls{SD-TMSR} for a long period of time (60 years) with different initial fissile materials and without any external feed of $^{233}$U to achieve the thorium fuel cycle transition. To do that, we investigate five types of initial fissile materials based on \gls{LEU}, Pu, and \gls{TRU} from LWR SF \cite{de2000scenarios}. Moreover, two different feed mechanisms are used as follows:
\begin{itemize}
	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}
This present paper is organized as follows: after an introduction about \gls{MSR} systems, the model description is discussed in section 2. Methodology and tools is descried in section 3. Extraction and feed mechanisms are addressed in section 4. Section 5 focuses on the results and discussion. Finally, section 6 highlights the conclusions.

>>>>

\section{Introduction}
The \gls{GIF} has defined eight technology goals for the next generation 
nuclear systems. These goals are: safety and reliability, economics, 
sustainability, non-proliferation and physical protection 
\cite{doe2002technology}. The \gls{MSR} has many advantages that consistent 
with \gls{GIF}'s goals, for example, liquid fuel, inherent safety, online 
reprocessing and refueling, excellent neutron economy and near atmospheric 
pressure in a primary loop \cite{siemer2015molten,rosenthal1970molten}. 
Thus, the \gls{GIF} selected \gls{MSR} as one of the promising Generation-IV 
reactors \cite{doe2002technology,pioro2016handbook}.
In the \gls{MSR}, the fuel is dissolved in a molten salt (e.g., LiF or NaCl). 
This liquid fuel salt (e.g., LiF-BeF$_2$-ThF$_4$-$^{233}$UF$_4$) constantly 
circulates through the core and allows transferring fission heat from reactor 
core to heat exchanger.

The Single-fluid Double-zone Thorium-based Molten Salt Reactor (SD-TMSR-2,250 
MW$_{th}$) was introduced by the \gls{CAS} \cite{li_optimization_2018}. The 
SD-TMSR 
is a graphite-moderated thermal-spectrum \gls{MSR} operating in Th/$^{233}$U 
fuel cycle. In the SD-TMSR the fissile and fertile elements are integrated 
into the same salt. In addition, the active core is divided into two zones, 
the radius of the fuel channels in the outer zone is modified to be larger 
than the radius of the fuel channels in the inner zone to improve the breeding 
ratio \cite{nuttin2005potential,li_optimization_2018}.

Historically, the thermal-spectrum \gls{MSR} was designed for the Th/$^{233}$U 
fuel cycle \cite{rykhlevskii2019modeling,nuttin2005potential,
merle2004scenarios,rosenthal1970molten}. This design assumes that we have 
fissile $^{233}$U inventory to startup new \glspl{MSR}. But $^{233}$U does not 
exist in the Earth's crust and can be produced from fertile $^{232}$Th only in 
the nuclear reactor. Therefore, it is required to examine alternative fissile 
materials (e.g., $^{235}$U) to replace the $^{233}$U in the startup fuel 
composition \cite{betzler2016modeling,zou2018transition}. The thorium fuel 
cycle transition can be achieved after reaching the doubling 
time\footnote{Time required to produce enough amount of $^{233}$U to trigger a 
new SD-TMSR.} of $^{233}$U because in this case all startup fissile material 
is being substituted by newly produced $^{233}$U.

Betzler \emph{et al.} discussed the simulation of the startup of a MSBR unit 
cell with \gls{LEU} (19.79\%) and Pu from \gls{LWR} spent fuel (SF) as initial 
fissile materials \cite{betzler2016modeling}. They concluded that the 
plutonium vector extracted from LWR SF is the best alternative source 
to $^{233}$U because it has the highest ratio of fissile isotopes 
\cite{betzler2016modeling}. Zou \emph{et al.} introduced two approaches for 
the thorium fuel cycle transition in \gls{TMSR}: in-core transition and 
ex-core transition. Historically, the TMSR is launched with existing fissile 
material and thorium as a fertile material; then the $^{233}$U bred from 
thorium is rerouted into the core to maintain criticality. In contrast, the 
new approaches tends to store produced $^{233}$U out of the core until there 
is enough amount to start a new TMSR \cite{zou2018transition}.
Additionally, Zou \emph{et al.} studied the transitioning to thorium fuel 
cycle in a small modular Th-based molten salt reactor (smTMSR) using \gls{TRU} 
as startup fuel. They concluded that the transition to thorium fuel cycle can 
be achieved in thermal smTMSR with a proper fuel fraction 
\cite{zou2018preliminary}.
Heuer \emph{et al.} discussed the transition characteristics of the \gls{MSFR} 
under different launching scenarios (e.g., enriched uranium and TRU) 
\cite{heuer2014towards}.

Indeed, there are various researches that revolve around starting the 
\glspl{MSR} with fissile materials alternative to $^{233}$U. Many of these 
researches focus on the fast-spectrum \glspl{MSR} \cite{ashraf2019modeling, 
ashraf2018nuclear, rykhlevskii_fuel_2019, betzler_impacts_2019, 
heuer2014towards,fiorina2013investigation}, while little focus on 
thermal-spectrum \glspl{MSR} \cite{betzler2016modeling, zou2018preliminary, 
zou2018transition}. Nevertheless, starting the \gls{SD-TMSR} with other 
fissile materials (except $^{233}$U) was not studied before. Therefore, 
the main object of the present paper is to discuss the simulation of the 
\gls{SD-TMSR} operation for a lifetime-long period of time (60 years) with 
different initial fissile materials and without any external feed of $^{233}$U 
to achieve the thorium fuel cycle transition. We investigated five different  
initial fissile materials: \gls{LEU}, Pu, and \gls{TRU} from LWR SF 
\cite{de2000scenarios}. Moreover, two different feed scenarios were selected:
\begin{itemize}
	\item Continuous feed flow of thorium and $^{233}$U from \texttt{Pa-decay tank}, where the removal rate of $^{233}$Pa = feed rate of $^{233}$U. \cite{betzler2016modeling}.
	\item Continuous feed flow of (Heavy Metal (HM) except for Th) + all or part of $^{233}$U from \texttt{Pa-decay tank}.
\end{itemize}
This present paper is organized as follows: after an introduction about \gls{MSR} systems, the model description is discussed in section 2. Methodology and tools is descried in section 3. Extraction and feed mechanisms are addressed in section 4. Section 5 focuses on the results and discussion. Finally, section 6 highlights the conclusions.
